---
output:
  html_document: default
  word_document: default
---

Heart Disease Statistics Update
========================================================
This little demonstration report was written in R--Studio using the *RMarkown* and *KnitR* packages. The resultant markdown code was converted by *pandoc* (not an R package, but other opensource software) into the .docx format.

Key points
=========================
* Coronary heart disease (CHD), which includes heart attacks, is a leading cause of illness and death in Scotland.
* The number of new cases of CHD (incidence) has decreased over the past decade. The age and sex standardised incidence rate decreased from 361.7 per 100,000 in 2003/04 to 262.8 in 2012/13, a decrease of 27.3%.
* There has been a steady downward trend in deaths from CHD in Scotland, UK and Europe over the last 10 years with the mortality rate in Scotland falling by 43.6%.
* The reduction in death rates for CHD over the decade 2003-2012 has been seen in both the most and least materially deprived communities.
* The percentage reduction in deaths in the most deprived category (37.6%) over the last 10 years is larger than that in the least deprived category (29.0%).
* The difference in the death rate between the most and least deprived areas has also decreased over the last decade.
* For those admitted to hospital as an emergency with their first heart attack, the chances of surviving at least 30 days have improved over the last ten years from 84.4% to 91.8%.
* Although the number of prescriptions for drugs to treat cardiovascular disease (all diseases of the circulation, including CHD) increased by 25.8% in the last 10 years, the overall costs of prescriptions dispensed for cardiovascular drugs fell in 2012/13 to £111.7 million, a reduction of 29.1% on the previous year.
* This is the lowest cost for these drugs over the last ten years (since 2003/04).
* Costs may continue to reduce as more medicines become available in less expensive non-branded (generic) form.

Coronary Heart Disease (CHD)
==========================
In coronary heart disease, the blood supply to the heart is reduced or blocked. This can cause heart attacks or chest pain on exercise (angina).

Heart disease discharges
--------------------------
In the last decade the overall trend in the number of discharges from hospital with CHD has been decreasing. The 1976 European age and sex standardised discharge rate fell by 21.7% from 856.1 to 670.2 per 100,000 population.  

What you can do
===============
Embedding tables
---------------
You can automatically embed tables produced from the data. This code makes the table.
```{r table1, results='asis'} 
mydata <- data.frame (sex = c(rep("male",20), rep("female",10)), eye.colour = sample (c("blue","green"),30,replace = TRUE), hair.colour = sample (c("blond","brown"),30,replace = TRUE))
a<- table (mydata$sex, mydata$eye.colour)
```
and this code turns it into the correct markdown format for export to MS word via pandoc.
```{r table, results = 'asis'}
knitr::kable(a)
```

Embedding plots
---------------
You can embed plots. Here is an example, where I have specified with width and height in inches and the dots per inch. The default format for the image is windows metafile as we are exporting to word.
```{r figure_test, fig.width=5, fig.height=4, dpi = 600, fig.cap="the name of the plot"}
plot(cars)
```

Embedding results within a paragraph
------------------------------------
You can embed results from an analysis. For example the average speed in the built--in "cars" dataset in R is `r mean(cars$speed)` miles per hour, and the maximum speed was `r max (cars$speed)` miles per hour.

Embedding equations
---------------------------
$$(1-p)^{n} = \frac{1}{p}$$


Adding footnotes
-----------------
Adding footnotes is also straightforward.
We can also write footnotes[^1]. And another footnote[^2]
In the conversion to word these become endnotes.


You can edit this all you like, with track changes. Then it can be copied and pasted back in and re-run.


Footnotes on the next page
-----------------
Footnotes on the next page keep the same numbering[^3]


[^1]: hi, I'm a footnote
[^2]: This is the second footnote.
[^3]: regardless of the actual number you choose
